\begin{enumerate} %[label=(E\arabic*).]
\item 
\textbf{Coordinator}, National Knowledge Network (NKN) course on \textit{Blockchain Technology and Applications}, January 3-8, 2021, NKN, IIT Roorkee.

\item 
\textbf{Steering Chair}, The Fourth International Workshop on \textit{Smart Living with IoT, Cloud and Edge Computing (SLICE-2021} in conjunction with The 18th International Conference on Mobile Ad-Hoc and Smart Systems ( MASS - 2021)(ERA Rank: B), October 4-7, 2021, \textbf{Denver, CO, USA.}

\item 
\textbf{Coordinator}, Workshop on \textit{GPU Architectures}, October 6, 2021, NVIDIA.

\item 
\textbf{Coordinator}, IBM OpenPOWER Foundation (OPF) Workshop on \textit{HPC and Cloud}, July 16, 2021,  IBM OPF.

\item 
\textbf{Course Coordinator}, Online Training Programme On \textit{Full Stack Web Development}, December 2-10, 2020 (EICT Academy, IIT Roorkee).

\item 
\textbf{Program Chair, Organizing Chair, and Web Chair}, The 17th IEEE International Conference on \textit{Mobile Ad-Hoc and Smart Systems (MASS 2020)} \textbf{(ERA Rank: B)}, December 10-13, 2020 (\textbf{IEEE Computer Society}), IIT Roorkee.

\item 
\textbf{Steering Chair}, The Third International Workshop on \textit{Smart Living with IoT, Cloud and Edge Computing (SLICE-2020} in conjunction with The 17th International Conference on Mobile Ad-Hoc and Smart Systems ( MASS - 2020)(ERA Rank: B), December 10-13, 2020 (\textbf{IEEE Computer Society}), IIT Roorkee.

\item 
\textbf{Course Coordinator}, One-Week Faculty Development Program on \textit{Cloud Computing and its Applications}, September 16-20, 2019 (EICT Academy, IIT Roorkee).

\item 
\textbf{Course Coordinator}, Online Summer Training Programme On \textit{Ethical Hacking and Cyber Security}, August 19-September 1, 2020 (EICT Academy, IIT Roorkee).

\item 
\textbf{Organizing Partner}, 2019 International Summer School on  \textit{Future Internet Architecture Security}, June 17-21, 2019, \textbf{University of Paduva, Paduva, Italy.}

\item 
\textbf{General Chair, and Session Chair}, Second IEEE International Workshop on \textit{Smart Living with IoT, Cloud and Edge Computing (SLICE-2019)} in conjunction with The Fourth IEEE International Conference on Fog and Mobile Edge Computing (FMEC 2019), June 10-13, 2019, \textbf{Rome, Italy.}

\item 
\textbf{Course Coordinator}, Workshop on \textit{OpenPOWER and AI}, February 6, 2019, IBM, Bangalore.

\item 
\textbf{Course Coordinator}, Workshop on \textit{IoT and Cloud Fundamentals for Cyber Security Cell, Information Technology Development Authority, Department of IT, Government of Uttarakhand.}, February 18, 2019, EICT \& Cognizance 2019, IIT Roorkee.

\item 
\textbf{Course Coordinator}, One-Week Faculty Development Program on \textit{IoT, What and How?}, December 24 – 28, 2018 (EICT Academy, IIT Roorkee).

\item 
\textbf{Course Coordinator}, One-Week Faculty Development Program on \textit{High Performance Computing and Deep Learning}, October 21-25, 2018 (EICT Academy, IIT Roorkee).

\item 
\textbf{General Chair}, second International Workshop on \textit{Data Science Engineering and Its Applications (DSEA-2018)} in association with The Fifth International Conference on Internet of Things: Systems, Management and Security (IoTSMS 2018), October 15-18, 2018, \textbf{Valencia, Spain.}

\item 
\textbf{General Chair}, First International Workshop on \textit{Smart Living with IoT, Cloud and Edge Computing (SLICE-2018)} in conjunction with The Third IEEE International Conference on Fog and Mobile Edge Computing (FMEC 2018), April 23-26, 2018, \textbf{Barcelona, Spain.}

\item
\textbf{Course Coordinator}, One-Week Faculty Development Program on \textit{Internet of Things}, January 13-17, 2018 (EICT Academy, IIT Roorkee)

\item
\textbf{Course Coordinator}, One-Week Short Course on \textit{Recent Trends in Network Security}, January 8-12, 2018 (ISEA Project, Phase-II \& EICT Academy, IIT Roorkee) (Invited 3 international speakers)

\item
\textbf{Course Coordinator}, Two-weeks Faculty Development Program on \textit{Computer Networks and Security}, May 24th - June 2nd, 2017 (EICT Academy, IIT Roorkee)

\item
\textbf{Course Coordinator}, One-week Short Course on \textit{Recent Trends in Network Security}, December 14-18, 2016 (ISEA Project, Phase-II)

\item
\textbf{Course Coordinator}, One-week Short Course on \textit{Recent Trends in Network Security}, February 1-5, 2016. (ISEA Project, Phase-II)

\item
\textbf{Organizing Committee Member (CSE)}, Conference on \textit{Recent Advances in Electronics and Computer Engineering (RAECE)}, IIT Roorkee, February 14-15, 2015.

\item
\textbf{Faculty Coordinator}, \textit{Code.fun.do – 24-hour hackathon, Microsoft, ACM IITR Students Chapter}, Dept. of CSE, February 6-8, 2015

\item
\textbf{Faculty Coordinator}, ACM one-day workshop on “\textit{Business Process Simulation}”, (17th January, 2015), Prof. D.S. Broca, XLRI, Jhamshedpur

\item
\textbf{Faculty Coordinator}, ACM inaugural lecture on “\textit{Emerging Trends in Cloud Computing}” (12th April 2014), Prof. Janakiram D, IIT Madras 

\item
\textbf{Faculty Coordinator}, Asian Programming Contest – 2014 (29th March, 2014)

\item
\textbf{Convener}, QIP Short Term Course on “\textit{Developments and Challenges in Cloud Computing}” (10-14 June, 2013)

\item
\textbf{Convener}, One-day workshop on\textit{ High Performance Computing}. June, 2012

\item
\textbf{Organizing Member}, Two-day workshop on\textit{ Cloud Computing and Security Issues}, 12-13 July, 2012, Osmania University, Hyderabad, India.

\item
\textbf{Convener}, National Level Students Technical Symposium (Paper Presentation Competition) , “ABHISARGA-2004” (23rd – 24th Sept., 2004) 

\item
\textbf{Convener}, National Short Term Training Program on OOAD \& UML(18th – 22nd July, 2005) 

\item
\textbf{Convener}, National Short Term Training on Databases \& Oracle (9th – 13th March, 2006) 

\item
\textbf{Convener}, State Level Competitions for INFOSYS campus connect students, ASPIRATIONS-2020 (14th August, 2007) 

\item
\textbf{Convener}, Second Alumni Meet (23rd February, 2008) 

\item
\textbf{Acted as Chairperson}, Advisor or Member for various events organized at National level or State level.

\end{enumerate}