\begin{flushleft}
	\textbf{\textcolor{magenta}{Books Authored}} 
\end{flushleft}


\begin{enumerate}%[label=(B\arabi
\item%[B1.]
Prachi Deshpande, S. C. Sharma, \textbf{Sateesh K. Peddoju},
\lq\lq \emph{Security and Data Storage Aspect in Cloud Computing},\rq\rq\, \textbf{Springer} Series in
Studies in Big Data, Springer--Verlag, Berlin--Heidelberg,
Germany, 2018. \\DOI: \url{https://doi.org/10.1007/978-981-13-6089-3}. Link: \url{https://www.springer.com/gp/book/9789811360886}.
\\(Dr. Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Dr. Prachi Deshpande)
\end{enumerate}

\begin{flushleft}
	\textbf{\textcolor{magenta}{Books Edited}} 
\end{flushleft}

\begin{enumerate}%[label=(B\arabi

	\item%[E3.]
M. Seetha, \textbf{Sateesh K. Peddoju}, Vishnu Pendyala, and Vedula VSSS Chakravarthy,, \lq\lq
\emph{Proceedings of 6th International Conference on Intelligent Computing and Communication - ICICC 2022},\rq\rq\, Advances in Intelligent Systems and Computing, \textbf{Springer}, 2023 (In Press).

	\item%[E3.]
Rajendra Prasad Mahapatra, \textbf{Sateesh K. Peddoju}, Sudip Roy, and Pritee Parwekar, \lq\lq
\emph{Proceedings of 8th International Conference on Recent Trends in Computing - ICRTC 2022},\rq\rq\, Lecture Notes in Networks and Systems, \textbf{Springer}, 2022 (In Press).

	\item%[E3.]
Ritika Mehra, Phayung Meesad, \textbf{Sateesh K. Peddoju}, and Dhajvir S. Rai, \lq\lq
\emph{Proceedings of International Conference, ICCISC 2022},\rq\rq\, Computational Intelligence and Smart Communication, \textbf{Springer}, 2022 \\DOI: \url{https://doi.org/10.1007/978-3-031-22915-2}.
		
		\item%[E4.]
\textbf{Sateesh K. Peddoju}, Guest Associate Editor, \lq\lq
\emph{Journal of Computer Science and Technology}, Special Section: IEEE MASS, \rq\rq\, \textbf{Springer} (SCIE, DBLP, Web of Science) (Impcat Factor: 2.58)

	\item%[E3.]
Sudhanshu Maurya, \textbf{Sateesh K. Peddoju}, 
 Badlishah Ahmad, and Ines Chihi, \lq\lq
\emph{Proceedings of Cyber Technologies and Emerging Sciences: ICCTES 2021},\rq\rq\, Lecture Notes in Networks and Systems, \textbf{Springer}, 2021. \\DOI: \url{https://doi.org/10.1007/978-981-19-2538-2}.

	\item%[E3.]
Rajendra Prasad Mahapatra, \textbf{Sateesh K. Peddoju}, Sudip Roy, Pritee Parwekar, and Lavika Goel, \lq\lq
\emph{Proceedings of 7th International Conference on Recent Trends in Computing - ICRTC 2021},\rq\rq\, Lecture Notes in Networks and Systems, \textbf{Springer}, 2021. \\DOI: \url{https://doi.org/10.1007/978-981-16-7118-0}.
	
	\item%[E2.]
C. M. Bhatt, \textbf{Sateesh K. Peddoju}, \lq\lq
\emph{Cloud Computing Systems and Applications in Healthcare},\rq\rq\, IGI Publisher, 2017. \\DOI: \url{https://doi.org/10.4018/978-1-5225-1002-4}.

\item%[E1.]
P. Suresh Kumar, \textbf{Sateesh K. Peddoju}, S. A. Moiz, Editorial Board of Proceedings of the National Workshop on Mobile Computing, Organized by Osmania University, Hyderabad held during 5th – 7th June, 2008.

\end{enumerate}
