\begin{enumerate}
	
\item 
\textbf{Coordinator}, Communications subgroup of Workgroup on “IoT Security” under e-Governance Standards and Guidelines, MeitY, Government of India. 

\item 
\textbf{Member}, Workgroup on “IoT Security” under e-Governance Standards and Guidelines, MeitY, Government of India. 

\item
\textbf{Member}, Cyber Crisis Management Plan (CCMP) and Crictical Information Infrastructure (CII) Policy, Computer Emergency Response Team (CERT)-Uttarakhand.

\item 
\textbf{Subject Expert}, Uttarakhand Public Service Commission.

\item
\textbf{Expert Member}, Uttarakhand Police Department (STF/CCPS) regarding Hackathon on Emerging Cyber Security Challenges.

\item 
\textbf{Jury Member}, Annual Convocation various Awards, 2020.

\item 
\textbf{Member}, Board of Studies, KITS, Kakatiya University, Warangal (for AI/ML UG Course).

\item 
\textbf{Member}, Board of Studies, Stanley College of Engineering, Osmania University, Hyderabad (for CSE UG Course).

\item
\textbf{Member}, Technical Committee, Next E-mail System of IITR.

\item
\textbf{Expert Member}, NSM  Group on Application Development, National Supercomputing Mission (NSM), Area: Geophysics and Oil Exploration.

\item
\textbf{Project  Review Steering Group Member}, National Mission on Education, through Information Communication \& Technology’ (NMEICT), Ministry of Human Resource Development (MHRD).

\item
\textbf{Expert Committee Member}, Uttarakhand Technical University, Dehradun.

\item
\textbf{Screening/Monitoring Committee Member}, DOEACC (NIELIT), India.

\item
\textbf{Expert Committee Member}, Mahamaya Technical University, Noida, India.

\item 
\textbf{Expert Committee Member}, Graphic Era University, Dehradun, India.

\item
\textbf{Member of Confidential Work} in GATE – 2013. 

\item
\textbf{Member of Confidential Work in Integrated Common Entrance Test} (ICET) in the years 2007 and 2008.

\item
\textbf{Institute (IITR) Representative of JEE and GATE examinations}.

\item
\textbf{Panel Member of Judgment for various events/competitions}

\end{enumerate}





