\begin{enumerate} %[label=(T\arabic*).]
\item
\textbf{December 16, 2022:} Invited Talk in Online Faculty Development Programme on Cloud Computing and Its Applications: Opportunities and challenges, Dr. BR Ambedkar NIT Jalandhar, during December 16-20, 2022 (Topic: IoT and Cloud for Better Future).

\item
\textbf{November 21, 2022:} Invited Talk at Devbhoomi Uttarakhand University, Dehradun on November 21, 2022 (Topic: IoT and Edge Computing: Concepts and Use Cases).

\item
\textbf{December 18, 2021:} Keynote - \textit{International Conference on Cyber Technologies and Emerging Sciences (ICCTES 2021)}, GE Hill Univ., Bhimtal. During December 17-18, 2021 (Topic: Design and Development of Models for Mobile Malware Detection).

\item
\textbf{December 9, 2021:} Invited Talk in AICTE-ISTE Orientation/Refresher programme on \textit{IoT \& applications}, Govt. EC, Bikaner, during 09-15 December 2021 (Topic: Research Opportunities \& Challenges in IoT).

\item
\textbf{December 6, 2021:} Invited Talk in AICTE-ISTE Faculty Refresher on \textit{Embedded Systems, IoT, Pervasive Computing} at Talla Padmavathi College of Engineering, Warangal from December 6-11, 2021 (Topic: Introduction to Embedded Systems, IoT and Pervasive Computing).

\item
\textbf{November 23, 2021:} Panel Chair (Moderator) in \textit{DSCI SERI Conference - Panel Discussion} (Topic: Security and Scale, Volume \& Velocity … Security Paradigm in Cloud).

\item
\textbf{November 18, 2021:} Invited Talk in \textit{Web based Technology program on Cloud Computing at BEL Academy for excellence}, Nalanda, November 16-18, 2021 (Topic: Security and Privacy issues in the Cloud).

\item
\textbf{October 25, 2021:} Invited Talk in Five-Day ATAL FDP on \textit{Internet of Things and Human-Computer Interaction}, NIT Goa, 25-29 October 2021 (Topic: IoT Overview and Advances).

\item
\textbf{October 22, 2021:} Invited Talk in ATAL - FDP on \textit{Cybersecurity \& Digital Forensics}, VRSEC Vijayawada, 26-30 July, 2021. (Topic: Cyber Security & Challenges).

\item
\textbf{October 19, 2021:} Invited Talk in ATAL FDP on \textit{Recent Trends in Cyber Security \& Forensics} from 18th-28th Oct 2021. (Topic: Wireless and IOT Security).

\item
\textbf{October 18, 2021:} Invited Talk in ATAL FDP on \textit{Cloud Forensics: Techniques, Challenges and Research Directions} held at NIT Sikkim on 18-22 October 2021 (Topic: Cloud Security and IDS in Virtual Firewall).

\item
\textbf{September 30, 2021:} EICT ISEA FDP on \textit{Information Security}, IIT Roorkee, September 27 - October 1, 2021,(Topic: IoT Security).

\item
\textbf{September 28, 2021:} Invited Talk in EICT ISEA FDP on \textit{Information Security}, IIT Roorkee, September 27 - October 1, 2021,(Topic: Cloud Security).

\item
\textbf{September 12, 2021:} Keynote - \textit{1st International Conference on Applied Mathematics, Modeling and Simulation in Engineering (AMSE) 2021}, Stanley College of E\&T for Women, Hyderabad, September 12, 2021 (Topic: Design and Development of Models for Mobile Malware Detection).

\item
\textbf{September 7, 2021:} Invited Talk in \textit{Induction Programme} 2021, SRM Noida, September 7, 2021 (Topic: Internet of Things).

\item
\textbf{August 27, 2021:} Invited Talk in ATAL FDP on \textit{A Blend of IoT, Cyber Security and Blockchain} conducted by NIT Silchar from 23rd to 27th August 2021. (Topic: IoT Security).

\item
\textbf{July 26, 2021:} Invited Talk in ATAL - FDP on \textit{Cybersecurity \& Digital Forensics}, VRSEC Vijayawada, 26-30 July, 2021. (Topic: Cyber Security & Challenges).

\item
\textbf{July 21, 2021:} Invited Talk in EICT course on \textit{Blockchain and IoT}, NIT Warangal \& Vaasavi CoE, Hyderabad, during July 12-22, 2021 (Topics: 1. IoT \& Edge Computing, 2. IoT Security).

\item
\textbf{July 19, 2021:} Invited Talk in Faculty Development Program on \textit{Cloud Computing Security Challenges and Solutions}, SCMS School of E\&T,  Karukutty, Kerala, held during July 19-24, 2021 (Topic: Cloud Security).

\item
\textbf{June 28, 2021:} Invited Talk in ATAL FDP on  \textit{Soft Computing, Machine Learning, Applications} held during  June 24- June 28, 2021, NIT Warangal \& LKBR CoE, Hyderabad, India (Topic: Machine Learning for Mobile Security).

\item
\textbf{June 22-23, 2021:} Invited Talk in QIP STC on \textit{Software Defined Networks and its Applications} held during  June 22- July 2, 2021, IIT Bhubaneswar, India (Topics: 1. Introduction to Cloud Computing and Security, and 2. Introduction to IoT and Mobile Security).

\item
\textbf{March 18, 2021:} Guest Talk in Online Induction—Refresher program on \textit{Recent Trends in Embedded Systems} held during  March 18—24, 2021, KITS, Ramtek, Maharastra, India.

\item
\textbf{March 12, 2021:} Invited Talk in TEQIP—III Sponsored Five Days Online Faculty Development Programme on \textit{Next Generation Computing and Networking} held during  March 08—12, 2021 which is being organized by the Department of Computer Science \& Engineering, NIT Uttarakhand, India.

\item
\textbf{March 08, 2021:} Guest Talk in FDP Program on On \textit{Advancements in Cyber Security} held during  8th March 2021 — 12th March 2021, The ICFAI Foundation for Higher Education (IFHE), Hyderabad, Telangana, India.

\item
\textbf{February 2, 2021:} Guest Talk on \textit{Internet of Things: Mathematical Relevance}, Geethanjali College of Engineering and Technology, Hyderabad, Telangana, India.

\item
\textbf{January 19, 2021:} Invited Talk in AICTE Training and Learning (ATAL) sponsored online FDP on \textit{Cyber Security} held during January 18-22, 2021, Osmania University, Hyderabad, Telangana, India.

\item
\textbf{Jan 9-10, 2021:} Invited Talk in FDP on \textit{Cyber Security} held during January 2—11, 2021, NIT Warangal and Vel Tech, Tamil Nadu, India.

\item
\textbf{December 21, 2020:} Invited Talk in One Week AICTE sponsored Short Term Training Programme on \textit{Challenges and Applications on Cyber—Physical Systems} Phase—III from 21h — 28th Dec—2020 Organized by Department of Computer Science and Engineering, School of Engineering \& Technology, GIET University, Gunupur, Odisha, India.

\item
\textbf{Nov/Dec 2020:} Guest Talk in Faculty Development Program (FDP) under AQIS 2019—20 Session during AICTE sponsored FDP on \textit{Emerging Trends in Deep Learning and its Applications}, Dr. D. Y. Patil Institute of Technology, Pimpri, Pune, Maharastra, India.

\item
\textbf{November 16, 2020:} Invited Talk in 5-Days Faculty Development Programme (FDP) on \textit{Cyber Security Analytics and Cyber Forensics} during November 16-20, 2020, Saintgits College of Engineering, Kottayam, Kerala, India.

\item
\textbf{November 9, 2020:} Invited Talk in 5-days Faculty Development Program on \textit{Internet of things}  organized by ECE Department  sponsored by AICTE ATAL academy during November 9-13, 2020, JNTUA College of Engineering Kalikiri, Andhra Pradesh, India.

\item
\textbf{November 4, 2020:} Invited Talk in ISEA sponsored one-week webinar on \textit{Cloud and Network Security Mechanisms} organized by the Department of Computer Science and Engineering, between 2nd November 2020 to 6th November 2020, IIT(ISM) Dhanbad, Jharkhand, India.

\item
\textbf{October 10, 2020:} Invited Talk in ISEA Short Term Course on \textit{Cyber Security and Cryptography} during October 07—11, 2020, IT Roorkee, Uttarakhand, India.

\item
\textbf{September 21, 2020:} Invited Talk in International Conclave on \textit{Recent Advances in Computer Science (ICRACS-2020)} during September 21st—25th, 2020, ANURAG University, Hyderabad, Telangana, India.

\item
\textbf{September 19, 2020:} Invited Talk in RGPV TEQIP—III \textit{online interactive session of Ph.D. Research Scholars} in computer science engineering, Rajiv Gandhi Proudyogiki Vishwavidyalya (RGPV), Madhya Pradesh, India.

\item
\textbf{September 7, 2020:} Invited Talk in Online - AICTE Training And Learning (ATAL) Faculty Development Programme (FDP) on \textit{CLOUD COMPUTING}   during September 7-11,  2020, Vaagdevi College of Engineering, Warangal, Telangana, India.

\item
\textbf{March 2—7, 2020:} Course Lectures @ Adjunct Faculty of \textit{Cloud Computing (CS4L018)}, for B.Tech and M.Tech students, School of Electrical Sciences, IIT Bhubaneswar, India.

\item
\textbf{Invited Talk:} \textit{Mobile Security: Issues and Challenges}, on March 3, 2020, NISER, Bhubaneshwar, Odisha, India.

\item
\textbf{February 27, 2020:} Guest Talk on \textit{Cloud/Edge Computing for Mobile Devices}, JNTU Jagityal, Karimnagar, T.S., India.

\item
\textbf{January 7, 2020:} Guest Talk on \textit{Mobility Challenges in Mobile Edge Computing}, IDRBT, Hyderabad, T.S., India.

\item
\textbf{December 23, 2019:} Guest Talk on \textit{Edge of Internet of Everything}, CBIT, Hyderabad, T.S., India.

\item
\textbf{December 16, 2019:} Keynote Talk on \textit{Advances in IoT}, KITS, Warangal, T.S., India.

\item
\textbf{Invited Talk:} \textit{Smart Systems and Smart Security}, on November 18, 2019, DTU, Delhi, India.

\item
\textbf{Keynote Talk:} \textit{Smart Devices and Smart Criminals}, on November 18, 2019, DTU, Delhi, India.

\item
\textbf{Invited Talk:} \textit{Cloud and Edge Computing for Mobile/IoT Devices}, on November 12, 2019, NIT, Karnataka, India.

\item
\textbf{Invited Talk:} \textit{Cloud and Edge Computing for ISRO Scientists}, on October 25, 2019, NRSC, Hyderabad, T.S., India.

\item
\textbf{Keynote Talk:} \textit{Trade-off Approach for Energy Efficiency and Service Availability in Mobile Edge Computing}, International Conference on Innovative Sustainable Computational Technologies (CISCT-2019) (IEEE Co-sponsored) scheduled on October 11, 2019, Dehradun, India.

\item
\textbf{Invited Talk:} \textit{Cloud and Emerging Technologies}, Guest lecture on Cloud and Emerging Technologies, on October 11, 2019, Dept. of MCA, DIT University, Dehradun, India.

\item
\textbf{Keynote Talk:} \textit{Advances in Cloud Computing}, One-week National Workshop on AWS Cloud Technology, on September 07, 2019, Shri Mata Vaishno Devi University, Katra, Jammu, India.

\item
\textbf{Keynote Talk:} \textit{Cloud, IoT, and Edge Computing}, National IEEE Student Workshop on Internet of Things: Devices to Cloud, on August 29, 2019, Dept. of IT, DIT University, Dehradun, India.

\item
\textbf{Invited Talk:} \textit{Distributed Systems and Blockchain: Preliminaries}, DST Sponsored FDP on Blockchain Technology and its Applications, on July 08, 2019, NIT Hamirpur, India.

\item
\textbf{Multiple Talks:} \textit{IoT Protocols, Healthcare IoT, Edge Computing, and Edge Assisted LEWS}, DST Sponsored FDP on Sensor Networks and IoT, on June 28-29, IIT Dhanbad, India.

\item
\textbf{Invited Talk:}\textit{Virtual Infrastructures and Deployment of Security Mechanisms}, at 2019 International Summer School on \textit{Future Internet Architecture Security}, on 18th June, 2019, Department of Mathematics, \textbf{University of Paduva, Paduva, Italy}.

\item
\textbf{Invited Talk:} \textit{Mobile Security - Challenges}, for B.Tech and M.Tech students, on May 20, 2019, NIT Rourkela, India.

\item
\textbf{Course Lectures @ Adjunct Faculty:} \textit{Cloud Computing (CS4L018)}, for B.Tech and M.Tech students, during March 18-24, 2019, School of Electrical Sciences, IIT Bhubaneswar, India.

\item
\textbf{Keynote Talk:} \textit{Machine Learning for Mobile Security}, on March 16, 2019 at 3rd International Conference on Data Engineering and Communications Technologies (ICDECT-2019), Hyderabad, India.

\item
\textbf{Valedictory Talk:} \textit{Edge Computing - Motivation for Research}, on February 8, 2019 at STC on IOT with Cloud Applications, Shri Mata Vaishno Devi University, J\&K, India.

\item
\textbf{Inaugural Talk:} \textit{OpenPOWER and Cloud: Case Studies}, on February 6, 2019 at Workshop on OpenPOWER and AI, IBM, Bangalore, India.

\item
\textbf{Keynote Talk:} \textit{Research Directions in IoT and Cloud}, on 12th January, 2019 at FDP on Internet of Things (IoT) with Cloud Applications, Graphic Era University, Dehradun, UK, India.

\item
\textbf{Speaker for various sessions:} \textit{IoT Applications Scenarios, IoT and Cloud, IoT Protocols, Advances in IoT, Edge Computing}, during December 24-28, 2018 at FDP on Internet of Things (IoT): What and How?, E \& ICT Academy, IIT Roorkee, Roorkee, UK, India.

\item
\textbf{Invited Speaker:} \textit{Motivation and Research Advises to Faculty of Computer Science}, on December 6, 2018 at Stanley College of Engineering \& Technology for Women, Hyderabad, TS, India.

\item
\textbf{Speaker for various sessions:} \textit{Parallel Programming, and HPC Case Studies}, on October 22 and 25, 2018 at FDP on High Performance Computing  and Deep Learning, E \& ICT Academy, IIT Roorkee, Roorkee, UK, India.

\item
\textbf{Speaker for various sessions::} \textit{IoT Applications Scenarios, and Advances in IoT}, on January 13 and 17, 2018 at FDP on Internet of Things (IoT), E \& ICT Academy, IIT Roorkee, Roorkee, UK, India.

\item
\textbf{Invited Talk:} \textit{The Role of Cloud Computing in Big Data Analytics}, on 9th January, 2018 at STTP on Big Data Analytics and Related Technologies, National Institute of Technology Raipur, Chattisgarh, India.
\item
\textbf{Invited Talk:} \textit{The Role of Cloud Computing in Big Data Analytics}, on 9th January, 2018 at STTP on Big Data Analytics and Related Technologies, National Institute of Technology Raipur, Chattisgarh, India.
\item
\textbf{Invited Talk:} \textit{Energy Efficiency and Seamless Service Provisioning in Mobile Cloud Computing}, on 19th October, 2017, University at Albany, State University of New York (SUNY), USA. 

\item
\textbf{Invited Talk and Chief Guest:} \textit{Parallel Computing Performance and Big Data Programming}, on 20th February 2016 at FDP on Parallel Computing, Feb 11-20, 2016, National Institute of Technology, Warangal, India.

\item
\textbf{Tutorial Session}, \textit{IoT and Cloud}, National Conference on Big Data Analytics \& Cloud Computing, Department of CSE, University College of Engineering(A), 29-31 December 2015, Osmania University, Hyderabad, India.

\item
\textbf{Chief Guest and Keynote Speaker}, \textit{Mobile \& Cloud Computing}, ASTRA-2k15, 27th \& 28th November 2015, Vaagdevi College of Engineering, Warangal, India.

\item
\textbf{Invited Speaker}, \textit{Cloud Computing and its Research}, Two-day workshop on Cloud Computing, TEQIP-II, 27-28, October, 2015, Government Engineering College, Bikaner, Rajasthan, India.

\item
\textbf{Invited Speaker}, \textit{Attack Scenarios in Cloud Computing}, Symposium on Cloud Computing and Digital Forensics, 4th September, 2015, BITS Pilani University, Hyderabad Campus, India.

\item
\textbf{Chief Guest and Chairperson of a Technical Session} and Plenary Session on \textit{Cloud Computing Research} of International Conference on Science and Technology 2015 for its conference track Computer Science February 27-28, 2015 organized by SRMS College of Engineering and Technology Bareilly, UP, India

\item
\textbf{Tutorial Session}, \textit{Researching Cloud Computing using Cloudsim}, International Conference on Computing and Communication Technologies (ICCCT), 11-13, December, 2014, Dept. of CSE, Osmania University, Hyderabad, India

\item
\textbf{Invited Speaker}, \textit{Cloudsim}, 11 October, 2014, GurukulKangri University, Haridwar, India.

\item
\textbf{Speaker for various sessions} on topics like \textit{Fundamentals}, \textit{Virtualization}, \textit{Advances}, \textit{Mobile Cloud} during the self-organized program, QIP Short Term Course on \textit{Developments and Challenges in Cloud Computing}, 10-14 June, 2013, Department of CSE and QIP Center, IIT Roorkee, India.

\item
\textbf{Invited Speaker}, \textit{Opportunities and Challenges in Wireless Sensor Networks} (21st March, 2013), AICTE Faculty Development Program on \textit{Wireless Sensor Networks}, 18-22 March, 2013, Sri Guru GovindSinghji Institute of Engineering and Technology, Nanded, Maharastra, India.

\item
\textbf{Guest of Honor and Keynote Speaker}, \textit{Recent Trends in Cloud Computing} (20th March, 2013), AICTE Faculty Development Program on \textit{Cloud Computing and its Applications}, 20-24, Mar, 2013, PDA College of Engineering, Gulbarga, Karnataka, India

\item
\textbf{Guest of Honor and Invited Speaker}, \textit{Demonstration of Cloud Computing Models} (20th March, 2013), AICTE Faculty Development Program on \textit{Cloud Computing and its Applications}, 20-24, Mar, 2013, PDA College of Engineering, Gulbarga, Karnataka, India

\item
\textbf{Keynote Speaker}, \textit{Importance of Simulations in Networking} (15th February, 2013), Faculty Development Program on \textit{Network Simulator NS—2}, AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, \textit{Wireless Simulations in NS—2} (15th February, 2013), Faculty Development Program on \textit{Network Simulator NS—2}, AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, \textit{Demonstration of Wireless environment using NS-2} (16th February, 2013), Faculty Development Program on \textit{Network Simulator NS-2}, AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, \textit{Results, Analysis, and Graphs of Wireless environment using NS-2} (16th February, 2013), Faculty Development Program on \textit{Network Simulator NS-2}, AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, \textit{Advances in IRS – Extensions to Cloud Computing} (28th January, 2013), DST Workshop on \textit{Information Retrieval Systems}, 28-29, January, 2013, Varadha Reddy Engineering College, Warangal, A.P., India.

\item
\textbf{Chief Guest and Invited Speaker}, \textit{Recent Trends in Mobile Cloud Computing}, Workshop on Recent Trends in Cloud Computing, 3-4, August, 2012, KPR Institute of Technology, Coimbatore, Tamil Nadu, India.

\item
\textbf{Chief Guest and Keynote Speaker}, \textit{Mobile Cloud Computing – Advances and Challenges}, Joint UACEE International Conference on Pervasive Computing and Communications (PCC 2012) and Second International Conference on Computing, Control and Communication (CCN-2012), 17th June, 2012, NCR-Delhi, India

\item
\textbf{Invited Speaker}, \textit{Wireless Networks and NS-2} (2nd June, 2012), Workshop on Simulation Software/Tools, 1st – 2nd June, 2012, Noida Institute of Engineering and Technology, NCR-Delhi, India

\item
\textbf{Invited Speaker}, \textit{MANETs and NS-2} (26th February, 2012), Workshop on NS-2 held during 25th – 26th February, 2012, Graphic Era University, Dehradun, U.K., India.

\item
\textbf{Chief Guest and Keynote Speaker}, \textit{Recent Advances in Mobile Communications} (23rd Sept, 2011), National Symposium, SCINTELLACE 2k11. 23-24, Sept, 2011, JNT University, Cuddapah, India.

\item
\textbf{Invited Speaker}, \textit{Mobile Ad-hoc Networks} (6th June, 2008), National Workshop on Mobile Computing held during 5th – 7th June, 2008, Dept. of CSE, Osmania University, Hyderabad, India.

\item
\textbf{Invited Speaker}, \textit{Object Oriented Programming} (9th February, 2008), National Short-Term Training Program on \textit{UML \& Automata} held during   9-11, February, 2008, KITS, Singapur, Karimnagar, India.

\item
\textbf{Invited Speaker}, \textit{Simulations using NS-2} (9th January, 2008), Pre-workshop tutorial in National Workshop for Research Scholars on \textit{Mobile Ad hoc Networks: Issues and Challenges} held during 10th – 11th January, 2008, Dept. of CSE, Osmania University, Hyderabad, India.

\item
\textbf{Invited Speaker and Guest of Honor}, \textit{NS-2 Simulator} (30th June, 2007),  One-day National Seminar on \textit{Network Simulation using OPNET and NS-2} held on 30th June, 2007, Dept. of CSE, V.R. Siddhartha Engineering College, Vijayawada, India.

\item
\textbf{Invited Speaker}, \textit{Mobile Ad-hoc Networks – Overview} (23rd June, 2007),  Three-day National Seminar on \textit{Networks \& Security} held during 21st – 23rd June, 2007, Dept. of CSE, Srinidhi Institute of Science \& Technology, Ghatkesar, Hyderabad, India.

\item
\textbf{Guest of Honor and Invited Speaker}, \textit{MANET Simulators} (24th November, 2006), National Seminar on \textit{Mobile \& Pervasive Computing} during 24th – 25th Nov.,2006, PDA College of Technology, Gulburga, Karnataka, India.

\item
\textbf{Invited Speaker}, \textit{Mobile Communications and NS-2} (30th June – 1st  July , 2005), Three weeks National Refresher Course on Advanced Mobile Computing, Academic Staff College, J.N.T.U., Hyderabad.

\item
\textbf{Invited Speaker}, \textit{NS-2 Demo} (18th – 19th December, 2004), Three weeks National Refresher Course on Mobile Computing, Academic Staff College, J.N.T.U., Hyderabad, India.

\item
\textbf{Guest Lecture}, \textit{Problem Solving Techniques} (Oct, 2010 – Till date), Foundation Program (FP), INFOSYS Campus Connect (CC) at IEG – JKC, Vaagdevi College of Engineering, Warangal, India.

\item
\textbf{Guest Lecture}, \textit{Web Technologies} (Nov, 2008 – Jan, 2009), FP, INFOSYS CC at IEG – JKC, Vaagdevi College of Engineering, Warangal, India.

\item
\textbf{Guest Lecture}, \textit{Programming Fundamentals} (Aug, 2008, Oct, 2008), FP, INFOSYS CC at IEG – JKC, Vaagdevi College of Engineering, Warangal, India.

\item
\textbf{Guest Lecture}, \textit{Programming Fundamentals} (Jun, 2006, Apr, 2006, Jan, 2006), FP, INFOSYS CC at IEG – JKC,  KITS, Singapur, Karimnagar, India.



\end{enumerate}