\begin{enumerate}%[label=(J\arabic*)]
	\item
	Vikas Chouhan, \textbf{Sateesh K. Peddoju}, and Rajkumar Buyya \lq\lq \textit{dualDup: A secure and reliable cloud storage framework to deduplicate the encrypted data and key},\rq\rq\, Journal of Information Security and Applications (2022), Volume 69, September 2022, 103265 \emph{(SCIE, Scopus)(IF=4.96)}. \\DOI: \url{https://doi.org/10.1016/j.jisa.2022.103265}  \\(Vikas Chouhan is the Ph. D student working with Sateesh K. Peddoju)

 	\item
  Aparna Tomar, Preeti Mishra, Rahul Bisht, and \textbf{Sateesh K. Peddoju} \lq\lq \textit{A Step Towards Generation of DoS/DDoS Attacks Dataset for Docker-Centric Computing},\rq\rq\, International Journal of Mathematical, Engineering and Management Sciences (2022), Volume 7(1), 81-91, 2022 \\DOI: \url{https://doi.org/10.33889/ijmems.2022.7.1.006}  \\(Preeti Mishra is collaborator of Sateesh K. Peddoju. Other two are her students.)
 
 \item
	Vikas Chouhan, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Reliable verification of distributed encoded data fragments in the cloud.},\rq\rq\, J Ambient Intell Human Comput (2020). \emph{(SCIE, Scopus)(IF=3.662)}. \\DOI: \url{https://doi.org/10.1007/s12652-020-02610-x}  \\(Vikas Chouhan is the Ph. D student working with Sateesh K. Peddoju)
	
	\item
	Vikas Chouhan, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Investigation of Optimal Data Encoding Parameters based on User Preference for Cloud Storage},\rq\rq\, IEEE Access,\textbf{IEEE}, vol. 8, pp. 75105-75118, 2020. \emph{(SCIE, Scopus)(IF=4.098)}. \\DOI: \url{https://doi.org/10.1109/ACCESS.2020.2987999} \\(Vikas Chouhan is the Ph. D student working with Sateesh K. Peddoju)
	
	\item
	Anshul Arora, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{PermPair :  Android Malware Detection using Permission Pairs},\rq\rq\, IEEE Transactions on Information Forensics \& Security, \textbf{IEEE}, Vol. 15, pp. 1968-1982, 2020. \emph{(SCIE, Scopus)(IF=7.231)}. \\DOI: \url{https://doi.org/10.1109/TIFS.2019.2950134}  \\(Anshul Arora is the Ph. D student working with Sateesh K. Peddoju)

	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Agriculture-as-a-Service},\rq\rq\, {\textbf{IEEE} Potentials}, 40(6), 34-43, 2021. DoI: \url{https://doi.org/10.1109/MPOT.2015.2496327}  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

 	\item
	Aayush Vishnoi, Preeti Mishra, Charu Negi, and \textbf{Sateesh K. Peddoju} \lq\lq \textit{Android Malware Detection Techniques in Traditional and Cloud Computing Platforms: A State-of-the-Art Survey},\rq\rq\, {International Journal of Cloud Applications and Computing}, 11(4), 113-135, 2021. DoI: \url{http://doi.org/10.4018/IJCAC.2021100107}  \\(Preeti Mishra is a collaborator of Sateesh K. Peddoju. Others are her students.)
 
	\item
	V.C. Pandey, \textbf{Sateesh K. Peddoju}, and Prachi Deshpande, \lq\lq \textit{A Statistical and Distributed Packet Filter against DDoS Attacks in Cloud Environment},\rq\rq\, S{\={a}}dhan{\={a}} Journal, \textbf{Springer}, vol. 43, no. 3, pp. 32:1-9, 2018. \emph{(SCIE, JCR, Scopus)(IF=0.769)}. \\DOI: \url{https://doi.org/10.1007/s12046-018-0800-7}.  \\(Vikash Chandra Pandey did his M.Tech thesis work with Sateesh K. Peddoju, and Prachi Deshpande is the Ph. D student working with Sateesh K. Peddoju (Co-Supervisor))
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{An adaptive plant leaf mobile informatics using RSSC},\rq\rq\, Multimedia Tools and Applications, \textbf{Springer}, vol. 76, No. 20 pp. 21339-21363, 2017. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.158)}. \\DOI: \url{https://doi.org/10.1007/s11042-016-4040-8}.  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju} , and D. Ghosh, \lq\lq \textit{An efficient low vision plant leaf shape identification system for smart phones},\rq\rq\, Multimedia Tools and Applications, \textbf{Springer}, vol. 76, No. 5, pp. 6915-6939, 2017. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.158)}. \\DOI: \url{https://doi.org/10.1007/s11042-016-3309-2}.  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)
	
	\item
	S. Garg, \textbf{Sateesh K. Peddoju}, and A. K. Sarje, \lq\lq \textit{Network-based detection of Android malicious apps},\rq\rq\, International Journal of Information Security, \textbf{Springer}, vol. 16, No. 4, pp. 385-400, 2017. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.36)}. \\DOI: \url{https://doi.org/10.1007/s10207-016-0343-z}. \\(Shree Garg did her Ph. D thesis work with Dr. Anil K. Sarje.  Sateesh K. Peddoju is the colleague to Dr. Anil K. Sarje and is the Co-Supervisor to Shree Garg)
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Multi-resolution mobile vision system for plant leaf disease diagnosis},\rq\rq\, Signal, Image and Video Processing, \textbf{Springer}, Vol. 10, No. 2, pp. 379-388, 2016. \emph{(SCIE, JCR,  Scopus, DBLP)(IF=2.157)}. \\DOI: \url{https://doi.org/10.1007/s11760-015-0751-y}.  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)
	
	\item
	S. Garg, \textbf{Sateesh K. Peddoju}, and A. K. Sarje, \lq\lq \textit{Scalable P2P bot detection system based on network data stream},\rq\rq\, Peer-to-Peer Networking and Applications, \textbf{Springer}, Vol. 9, No. 6, pp. 1209-1225, 2016. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.604}. \\DOI: \url{https://doi.org/10.1007/s12083-016-0440-9}. \\(Shree Garg did her Ph. D thesis work with Dr. Anil K. Sarje.  Sateesh K. Peddoju is the colleague to Dr. Anil K. Sarje and is the Co-Supervisor to Shree Garg)
	
	\item
	P. Deshpande, S. Sharma, \textbf{Sateesh K. Peddoju}, and A. Abraham, \lq\lq \textit{Security and service assurance issues in Cloud environment},\rq\rq\, International Journal of System Assurance Engineering and Management, \textbf{Springer}, Vol. 9, No. 1, pp. 194-204, 2018 (Fist Online: 2016). \emph{(ESCI, Scopus, DBLP)(IF=2.02)}. \\DOI: \url{https://doi.org/10.1007/s13198-016-0525-0}.  \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)
	
	\item
	S. Sharma, U. S. Tim, S. Gadia, J. Wong, R. Shandilya, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Classification and comparison of NoSQL big data models},\rq\rq\, International Journal of Big Data Intelligence, \textbf{Inderscience}, Vol. 2, No. 3, pp. 201-221, 2015. \emph{(DBLP, ACM)}. \\DOI: \url{https://doi.org/10.1504/IJBDI.2015.070602}.
\\(Sugam Sharma, U. Sunday Tim, S. Gadia, J. Wong, R. Shandilya are the research collaborators to Sateesh K. Peddoju)	
	
	\item
	A. Ravi, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Handoff strategy for improving energy efficiency and cloud service availability for mobile devices}, \rq\rq\, Wireless Personal Communications, \textbf{Springer}, Vol. 81, No. 1, pp. 101-132, 2015. \emph{(SCIE, JCR, Scopus, ACM)(IF=1.2)}. \\DOI: \url{https://doi.org/10.1007/s11277-014-2119-y}. \\(Anuradha Ravi did her Ph. D Thesis with Sateesh K. Peddoju)
	
	
	\item
	P. Deshpande, S. Sharma, \textbf{Sateesh K. Peddoju}, and A. Abraham, \lq\lq \textit{Efficient multimedia data storage in cloud environment},\rq\rq\, Informatica, Vol. 39, No.4, pp. 431-442, 2015. \emph{(ESCI, Scopus, DBLP, ACM)}. \\Link: \url{http://www.informatica.si/index.php/informatica/article/download/1087/778} \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)
	
	\item
	K. Bhanot, \textbf{Sateesh K. Peddoju}, and T. Bhardwaj, \lq\lq \textit{A model to find optimal percentage of training and testing data for efficient ECG analysis using neural network},\rq\rq\, International Journal of System Assurance Engineering and Management, \textbf{Springer}, Vol. 9, No. 1, pp. 12-17, 2018 (Fist Online: 2015). \emph{(ESCI, Scopus, DBLP)}. \\DOI: \url{https://doi.org/10.1007/s13198-015-0398-7}.
\\ (Kartik Bhanot did his Internship with Sateesh K. Peddoju and Tushar Bhardwaj is the collaborator and equal contributor in the paper)
	
	\item
	P. Deshpande, S. Sharma, \textbf{Sateesh K. Peddoju}, and S. Junaid, \lq\lq \textit{HIDS: A host based intrusion detection system for cloud computing environment},\rq\rq\, International Journal of System Assurance Engineering and Management, \textbf{Springer}, Vol. 9, No. 3, 2018 (First Online: 2014) pp. 1-10, 2014. \emph{(ESCI, Scopus, DBLP)}. \\DOI: \url{https://doi.org/10.1007/s13198-014-0277-7}.  \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)
	
	
\end{enumerate}		