\begin{enumerate} %[label=(PHD\arabic*).]	
		\item Anuradha Ravi (Enroll. No. 11915001): \textit{Energy Efficient Seamless Service Provisioning in Mobile Cloud Computing}; Awarded: 28-12-2015
		\item Shitala Prasad (Enroll. No. 11915006): \textit{Mobile Vision system for Plant Leaf Analysis}; Co-supervisor: Prof. D. Ghosh (ECE, IITR); Awarded: 20-02-2016
		\item Shre Garg (Enroll. No. 10915010): \textit{Network Behavior Analysis Based Effective Detection Of Botnets}; Co-supervisor: Prof. Anil K. Sarje (CSE, IITR); Awarded: 26-02-2016
	\item Prachi Deshpande (Enroll. No. 11926012): \textit{Security And Storage Issues In Cloud Environment}; Co-supervisor: Prof. S. C. Sharma (IPT, IITR); Awarded: 26-05-2016
	\item Anshul Arora (Enroll. No. 14911009): \textit{Design and Development of Models for Mobile Malware Detection}; Status: Awarded: Viva Completed.
	\item Ajay Choudhary (Enroll. No. 14911016): \textit{Internet of Things (IoT) for Smart Agriculture}; Status: In Progress
	\item Vikas Chouhan (Enroll. No. 14911024): \textit{Cloud Storage Security}; Status: Submitted
	\item Animesh Kuity (Enroll. No. 15911001): \textit{High Performance Computing in Cloud - Container Design};	Status: In Progress	 	
	\item Surabhi Sharma (Enroll. No. 17911010): \textit{Messaging Protocols Design in Internet of Things (IoT) and Cloud}; Status: In Progress	
	\item Abdul Kadir (Enroll. No. 18911001), \textit{Machine Learning in Mobile Security}; Status: In Progress
	\item Rama Krishna Koppanati (Enroll. No. 19911003), \textit{Cyber Security - Blockchain - Mobile Security}; Status: In Progress
	\item Srivastava Parth Randhir Kumar (Enroll. No. 19911011), \textit{Machine Learning in IoT}; Status: In Progress
	\item Swati Singh (Enroll. No.20911011), \textit{Machine Learning in IoT}; Status: In Progress
	\item Shikha Arya (Enroll. No. 20911019), \textit{Machine Learning in IoT}; Status: In Progress
		\item Yoga B. S. (Enroll. No. ), \textit{IoT}; Status: In Progress
			\end{enumerate}