\begin{enumerate}

\item
\textbf{IEEE MASS 2020}, The 17th IEEE International Conference on \textbf{Mobile Ad-Hoc and Smart Systems (IEEE MASS 2020)}, December 10-13, 2020, (virtually), IIT Roorkee, India. 
	
\item
\textbf{IEEE FMEC 2019}, The Fourth IEEE International Conference on Fog and Mobile Edge Computing (FMEC 2019), June 10-13, 2019, Rome, Italy.

\item
\textbf{ACM ICPE 2019}, 24th ACM International Conference on Performance Engineering, April 8-14, 2019, IIT Bombay, India.

\item
\textbf{Microsoft AXLE 2019}, Academic Accelerators and Code Fun Do ++, February 5, 2019, Bangalore, India.

\item
\textbf{Google Faculty Institute 2018}, December 10-11, 2018, Delhi NCR, India.

\item
\textbf{Microsoft AXLE 2018}, Academic Accelerators and Code Fun Do ++, May 15, 2018, Hyderabad, India.

\item
\textbf{SC-15}, Supercomputing Conference, November 15-20, 2015, Austin, Texas, USA.

\item
\textbf{HP-CAST}, High Performance Computing Summit, September, 2015, Jaipur, India.

\item
\textbf{IEEE} Conference on High Performance Computing (\textbf{Hi-PC}), December, 2015, Bangalore, India.

\item
\textbf{HP-CAST}, High Performance Computing Summit, August, 2014, Pune, India.

\item
Two-day workshop on Cloud Computing and Security Issues, 12-13 July, 2012, Osmania University, Hyderabad, India.

\item
Two weeks course on Effective Teaching/Learning of Computer Programming. During: 28th June – 10th Jul, 2010, Organized by:\textbf{ I.I.T}, Bombay (Remote Center:\textbf{ N.I.T}, Warangal), Sponsored by: \textbf{ISTE}, India.

\item
Short term training program on Automation and Robotics, During: 6th – 18th July, 2009, Organized by: National Institute of Technology (\textbf{N.I.T}.), Warangal, Sponsored by: \textbf{MHRD}, India. 

\item
National Workshop on Mobile Computing, During:5th – 7th June, 2008. Organized by: Department of \textbf{CSE}, Osmania University, Hyderabad, Sponsored by: \textbf{TEQIP}, India. 

\item
National Workshop on Data Mining, During: 15th – 16th May, 2008. Organized by: Department of \textbf{CSE}, Osmania University, Hyderabad, Sponsored by: \textbf{TEQIP}, India. 

\item
Two day workshop on Mobile Ad-hoc Networks: Issues and Challenges, During: 10th – 11th Jan, 2008. Organized by: Department of \textbf{CSE}, Osmania University, Hyderabad, Sponsored by: \textbf{TEQIP}, India. 

\item
National Seminar on Emerging Trends in Physics – Celebration of Centenary of 1905, During: 12th – 13th Aug, 2005. Organized by: \textbf{KITS}, Singapur, Sponsored by: \textbf{IAPT}, India.

\item
Short Term Course on Web Design and Development. During 8th – 12th Dec, 2003, Organized by: Indian Institute of Technology (\textbf{I.I.T.}), New Delhi. Sponsored by: \textbf{AICTE-QIP}, India. 

\item
National Level Introductory School on Astronomy and Astrophysics. During: 15th – 19th Oct, 2001, Organized by: RajarshiShahuMahavidyalaya, Latur, Maharastra, Sponsored by: \textbf{IUCAA}, Pune, India.

\item
National workshop on \textbf{CADD}. During: 21st – 22nd Dec, 1997, Organized by: \textbf{KITS}, Warangal.

\end{enumerate}