
\begin{flushleft}
	\textbf{\textcolor{magenta}{Books Authored}} 
\end{flushleft}


\begin{enumerate}%[label=(B\arabi
\item%[B1.]
Prachi Deshpande, S. C. Sharma, \textbf{Sateesh K. Peddoju},
\lq\lq \emph{Security and Data Storage Aspect in Cloud Computing},\rq\rq\, \textbf{Springer} Series in
Studies in Big Data, Springer--Verlag, Berlin--Heidelberg,
Germany, 2018. \\DOI: \url{https://doi.org/10.1007/978-981-13-6089-3}. 
\\(Dr. Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Dr. Prachi Deshpande)
\end{enumerate}

\begin{flushleft}
	\textbf{\textcolor{magenta}{Books Edited}} 
\end{flushleft}

%\begin{enumerate}%[label=(B\arabi
\begin{etaremune}
	\item%[E3.]
M. Seetha, \textbf{Sateesh K. Peddoju}, Vishnu Pendyala, and Vedula VSSS Chakravarthy,, \lq\lq
\emph{Proceedings of 6th International Conference on Intelligent Computing and Communication - ICICC 2022},\rq\rq\, Advances in Intelligent Systems and Computing, \textbf{Springer}, 2023 (In Press).

	\item%[E3.]
Rajendra Prasad Mahapatra, \textbf{Sateesh K. Peddoju}, Sudip Roy, and Pritee Parwekar, \lq\lq
\emph{Proceedings of 8th International Conference on Recent Trends in Computing - ICRTC 2022},\rq\rq\, Lecture Notes in Networks and Systems, \textbf{Springer}, 2022 (In Press).

	\item%[E3.]
Ritika Mehra, Phayung Meesad, \textbf{Sateesh K. Peddoju}, and Dhajvir S. Rai, \lq\lq
\emph{Proceedings of International Conference, ICCISC 2022},\rq\rq\, Computational Intelligence and Smart Communication, \textbf{Springer}, 2022 \\DOI: \url{https://doi.org/10.1007/978-3-031-22915-2}.
		
		\item%[E4.]
\textbf{Sateesh K. Peddoju}, Guest Associate Editor, \lq\lq
\emph{Journal of Computer Science and Technology}, Special Section: IEEE MASS, \rq\rq\, \textbf{Springer} (SCIE, DBLP, Web of Science) (Impcat Factor: 2.58)

	\item%[E3.]
Sudhanshu Maurya, \textbf{Sateesh K. Peddoju}, 
 Badlishah Ahmad, and Ines Chihi, \lq\lq
\emph{Proceedings of Cyber Technologies and Emerging Sciences: ICCTES 2021},\rq\rq\, Lecture Notes in Networks and Systems, \textbf{Springer}, 2021. \\DOI: \url{https://doi.org/10.1007/978-981-19-2538-2}.

	\item%[E3.]
Rajendra Prasad Mahapatra, \textbf{Sateesh K. Peddoju}, Sudip Roy, Pritee Parwekar, and Lavika Goel, \lq\lq
\emph{Proceedings of 7th International Conference on Recent Trends in Computing - ICRTC 2021},\rq\rq\, Lecture Notes in Networks and Systems, \textbf{Springer}, 2021. \\DOI: \url{https://doi.org/10.1007/978-981-16-7118-0}.
	
	\item%[E2.]
C. M. Bhatt, \textbf{Sateesh K. Peddoju}, \lq\lq
\emph{Cloud Computing Systems and Applications in Healthcare},\rq\rq\, IGI Publisher, 2017. \\DOI: \url{https://doi.org/10.4018/978-1-5225-1002-4}.

\item%[E1.]
P. Suresh Kumar, \textbf{Sateesh K. Peddoju}, S. A. Moiz, Editorial Board of Proceedings of the National Workshop on Mobile Computing, Organized by Osmania University, Hyderabad held during 5th – 7th June, 2008.

%\end{enumerate}
\end{etaremune}

\begin{flushleft}
	{\textbf{\textcolor{magenta}{Journals}}}
\end{flushleft}

%\begin{enumerate}%[label=(J\arabic*)]
\begin{etaremune}
	\item
	Vikas Chouhan, \textbf{Sateesh K. Peddoju}, and Rajkumar Buyya \lq\lq \textit{dualDup: A secure and reliable cloud storage framework to deduplicate the encrypted data and key},\rq\rq\, Journal of Information Security and Applications (2022), Volume 69, September 2022, 103265 \emph{(SCIE, Scopus)(IF=4.96)}. \\DOI: \url{https://doi.org/10.1016/j.jisa.2022.103265}  \\(Vikas Chouhan is the Ph. D student working with Sateesh K. Peddoju)

 	\item
  Aparna Tomar, Preeti Mishra, Rahul Bisht, and \textbf{Sateesh K. Peddoju} \lq\lq \textit{A Step Towards Generation of DoS/DDoS Attacks Dataset for Docker-Centric Computing},\rq\rq\, International Journal of Mathematical, Engineering and Management Sciences (2022), Volume 7(1), 81-91, 2022 \\DOI: \url{https://doi.org/10.33889/ijmems.2022.7.1.006}  \\(Preeti Mishra is collaborator of Sateesh K. Peddoju. Other two are her students.)
 
 \item
	Vikas Chouhan, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Reliable verification of distributed encoded data fragments in the cloud.},\rq\rq\, J Ambient Intell Human Comput (2020). \emph{(SCIE, Scopus)(IF=3.662)}. \\DOI: \url{https://doi.org/10.1007/s12652-020-02610-x}  \\(Vikas Chouhan is the Ph. D student working with Sateesh K. Peddoju)
	
	\item
	Vikas Chouhan, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Investigation of Optimal Data Encoding Parameters based on User Preference for Cloud Storage},\rq\rq\, IEEE Access,\textbf{IEEE}, vol. 8, pp. 75105-75118, 2020. \emph{(SCIE, Scopus)(IF=4.098)}. \\DOI: \url{https://doi.org/10.1109/ACCESS.2020.2987999} \\(Vikas Chouhan is the Ph. D student working with Sateesh K. Peddoju)
	
	\item
	Anshul Arora, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{PermPair :  Android Malware Detection using Permission Pairs},\rq\rq\, IEEE Transactions on Information Forensics \& Security, \textbf{IEEE}, Vol. 15, pp. 1968-1982, 2020. \emph{(SCIE, Scopus)(IF=7.231)}. \\DOI: \url{https://doi.org/10.1109/TIFS.2019.2950134}  \\(Anshul Arora is the Ph. D student working with Sateesh K. Peddoju)

	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Agriculture-as-a-Service},\rq\rq\, {\textbf{IEEE} Potentials}, 40(6), 34-43, 2021. DoI: \url{https://doi.org/10.1109/MPOT.2015.2496327}  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

 	\item
	Aayush Vishnoi, Preeti Mishra, Charu Negi, and \textbf{Sateesh K. Peddoju} \lq\lq \textit{Android Malware Detection Techniques in Traditional and Cloud Computing Platforms: A State-of-the-Art Survey},\rq\rq\, {International Journal of Cloud Applications and Computing}, 11(4), 113-135, 2021. DoI: \url{http://doi.org/10.4018/IJCAC.2021100107}  \\(Preeti Mishra is a collaborator of Sateesh K. Peddoju. Others are her students.)
 
	\item
	V.C. Pandey, \textbf{Sateesh K. Peddoju}, and Prachi Deshpande, \lq\lq \textit{A Statistical and Distributed Packet Filter against DDoS Attacks in Cloud Environment},\rq\rq\, S{\={a}}dhan{\={a}} Journal, \textbf{Springer}, vol. 43, no. 3, pp. 32:1-9, 2018. \emph{(SCIE, JCR, Scopus)(IF=0.769)}. \\DOI: \url{https://doi.org/10.1007/s12046-018-0800-7}.  \\(Vikash Chandra Pandey did his M.Tech thesis work with Sateesh K. Peddoju, and Prachi Deshpande is the Ph. D student working with Sateesh K. Peddoju (Co-Supervisor))
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{An adaptive plant leaf mobile informatics using RSSC},\rq\rq\, Multimedia Tools and Applications, \textbf{Springer}, vol. 76, No. 20 pp. 21339-21363, 2017. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.158)}. \\DOI: \url{https://doi.org/10.1007/s11042-016-4040-8}.  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju} , and D. Ghosh, \lq\lq \textit{An efficient low vision plant leaf shape identification system for smart phones},\rq\rq\, Multimedia Tools and Applications, \textbf{Springer}, vol. 76, No. 5, pp. 6915-6939, 2017. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.158)}. \\DOI: \url{https://doi.org/10.1007/s11042-016-3309-2}.  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)
	
	\item
	S. Garg, \textbf{Sateesh K. Peddoju}, and A. K. Sarje, \lq\lq \textit{Network-based detection of Android malicious apps},\rq\rq\, International Journal of Information Security, \textbf{Springer}, vol. 16, No. 4, pp. 385-400, 2017. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.36)}. \\DOI: \url{https://doi.org/10.1007/s10207-016-0343-z}. \\(Shree Garg did her Ph. D thesis work with Dr. Anil K. Sarje.  Sateesh K. Peddoju is the colleague to Dr. Anil K. Sarje and is the Co-Supervisor to Shree Garg)
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Multi-resolution mobile vision system for plant leaf disease diagnosis},\rq\rq\, Signal, Image and Video Processing, \textbf{Springer}, Vol. 10, No. 2, pp. 379-388, 2016. \emph{(SCIE, JCR,  Scopus, DBLP)(IF=2.157)}. \\DOI: \url{https://doi.org/10.1007/s11760-015-0751-y}.  \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)
	
	\item
	S. Garg, \textbf{Sateesh K. Peddoju}, and A. K. Sarje, \lq\lq \textit{Scalable P2P bot detection system based on network data stream},\rq\rq\, Peer-to-Peer Networking and Applications, \textbf{Springer}, Vol. 9, No. 6, pp. 1209-1225, 2016. \emph{(SCIE, JCR, Scopus, DBLP, ACM)(IF=3.604}. \\DOI: \url{https://doi.org/10.1007/s12083-016-0440-9}. \\(Shree Garg did her Ph. D thesis work with Dr. Anil K. Sarje.  Sateesh K. Peddoju is the colleague to Dr. Anil K. Sarje and is the Co-Supervisor to Shree Garg)
	
	\item
	P. Deshpande, S. Sharma, \textbf{Sateesh K. Peddoju}, and A. Abraham, \lq\lq \textit{Security and service assurance issues in Cloud environment},\rq\rq\, International Journal of System Assurance Engineering and Management, \textbf{Springer}, Vol. 9, No. 1, pp. 194-204, 2018 (Fist Online: 2016). \emph{(ESCI, Scopus, DBLP)(IF=2.02)}. \\DOI: \url{https://doi.org/10.1007/s13198-016-0525-0}.  \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)
	
	\item
	S. Sharma, U. S. Tim, S. Gadia, J. Wong, R. Shandilya, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Classification and comparison of NoSQL big data models},\rq\rq\, International Journal of Big Data Intelligence, \textbf{Inderscience}, Vol. 2, No. 3, pp. 201-221, 2015. \emph{(DBLP, ACM)}. \\DOI: \url{https://doi.org/10.1504/IJBDI.2015.070602}.
\\(Sugam Sharma, U. Sunday Tim, S. Gadia, J. Wong, R. Shandilya are the research collaborators to Sateesh K. Peddoju)	
	
	\item
	A. Ravi, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Handoff strategy for improving energy efficiency and cloud service availability for mobile devices}, \rq\rq\, Wireless Personal Communications, \textbf{Springer}, Vol. 81, No. 1, pp. 101-132, 2015. \emph{(SCIE, JCR, Scopus, ACM)(IF=1.2)}. \\DOI: \url{https://doi.org/10.1007/s11277-014-2119-y}. \\(Anuradha Ravi did her Ph. D Thesis with Sateesh K. Peddoju)
	
	
	\item
	P. Deshpande, S. Sharma, \textbf{Sateesh K. Peddoju}, and A. Abraham, \lq\lq \textit{Efficient multimedia data storage in cloud environment},\rq\rq\, Informatica, Vol. 39, No.4, pp. 431-442, 2015. \emph{(ESCI, Scopus, DBLP, ACM)}. \\Link: \url{http://www.informatica.si/index.php/informatica/article/download/1087/778} \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)
	
	\item
	K. Bhanot, \textbf{Sateesh K. Peddoju}, and T. Bhardwaj, \lq\lq \textit{A model to find optimal percentage of training and testing data for efficient ECG analysis using neural network},\rq\rq\, International Journal of System Assurance Engineering and Management, \textbf{Springer}, Vol. 9, No. 1, pp. 12-17, 2018 (Fist Online: 2015). \emph{(ESCI, Scopus, DBLP)}. \\DOI: \url{https://doi.org/10.1007/s13198-015-0398-7}.
\\ (Kartik Bhanot did his Internship with Sateesh K. Peddoju and Tushar Bhardwaj is the collaborator and equal contributor in the paper)
	
	\item
	P. Deshpande, S. Sharma, \textbf{Sateesh K. Peddoju}, and S. Junaid, \lq\lq \textit{HIDS: A host based intrusion detection system for cloud computing environment},\rq\rq\, International Journal of System Assurance Engineering and Management, \textbf{Springer}, Vol. 9, No. 3, 2018 (First Online: 2014) pp. 1-10, 2014. \emph{(ESCI, Scopus, DBLP)}. \\DOI: \url{https://doi.org/10.1007/s13198-014-0277-7}.  \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)
	
	
%\end{enumerate}	
\end{etaremune}

\begin{flushleft}
	{\textbf{\textcolor{magenta}{Conferences}}}
\end{flushleft}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{enumerate}%[label=(C\arabic*).]	
\begin{etaremune}

    \item
    Surabhi Sharma and \textbf{Sateesh K. Peddoju} \lq\lq \textit{IoT-Cache: Caching Transient Data at the IoT Edge}, \rq\rq\, in 2022 IEEE 47th Conference on Local Computer Networks (LCN) (online), hybrid format (hosted in Edmonton, Canada), September 26-29, 2022, pp. 307-310, \underline{\textbf{ERA Rank: A}}, \textbf{IEEE Computer Society}. \\DOI: \url{https://doi.org/10.1109/LCN53696.2022.9843211}.
   \\(Surabhi Sharma is the Ph.D Student working with Sateesh K. Peddoju)

       \item
    Ajay Chaudhary and \textbf{Sateesh K. Peddoju} \lq\lq \textit{Impact of Clustering Algorithms and Energy Harvesting Scheme on IoT/WSN Infrastructures}, \rq\rq\, in 2021 IEEE 18th International Conference on Mobile Ad Hoc and Smart Systems (MASS) (online), Denver, CO, USA, 04-07 October 2021, pp. 603-608, \underline{\textbf{ERA Rank:B}}, \textbf{IEEE Computer Society}. \\DOI: \url{https://doi.org/10.1109/MASS52906.2021.00086}.
   \\(Ajay Chaudhary is the Ph.D Student working with Sateesh K. Peddoju)
    
    \item
    Nikunj Gupta, R. Ashiwal, B. Brank, \textbf{Sateesh K. Peddoju}, and D. Pleiter, \lq\lq \textit{Performance Evaluation of ParalleX Execution model on Arm-based Platforms}, \rq\rq\, in 2020 IEEE International Conference on Cluster Computing (CLUSTER) (online), Kobe, Japan, September 14-17, 2020, pp. 567-575, \underline{\textbf{ERA Rank:A}}, \textbf{IEEE Computer Society}. \\DOI: \url{https://doi.org/10.1109/CLUSTER49012.2020.00080}.
   \\(Nikunj Gupta and R. Ashiwal are the B.Tech. Final Year Students working with Sateesh K. Peddoju, Dirk Pleiter and B. Brank are the collaborators of Sateesh K.Peddoju)


       \item
    Anushka Joshi, \textit{Sateesh K. Peddoju}, and Mohit Pandey, \lq\lq \textit{Simulated Annealing Algorithm for Subsurface Shear Wave Velocity Investigation Using Ground Vibration Data}, \rq\rq\, in 7th International Conference on Recent Advances in Geotechnical Earthquake Engineering and Soil Dynamics (ICRAGEE), \textbf{Indian Institute of Science (IISc)}, Bangalore during July 13-16, 2020 \\DOI: \url{https://doi.org/10.1007/978-981-15-9984-2_3},  Lecture Notes in Civil Engineering, vol 117. Springer, Singapore. 
   \\(Anushka Joshi is the internship student worked with Sateesh K. Peddoju, Mohit Pandey is the collaborator of Sateesh K.Peddoju)
    
		\item
	A. Anshul, \textbf{Sateesh K. Peddoju}, V. Chouhan, A. Choudhary, \lq\lq \textit{Hybrid Android Malware Detection by Combining Supervised and Unsupervised Learning},\rq\rq\, in The 24th Annual Conference on Mobile Computing and Networking (MobiCom - 2018), New Delhi, India, October 29 - November 2, 2018, \underline{\textbf{ERA Rank:A*}}, \textbf{ACM SigMobile}. \\DOI: \url{https://doi.org/10.1145/3241539.3267768}. \\ (Anshul Arora, V. Chouhan, and A. Choudhary are the Ph. D students with Sateesh K. Peddoju)

	
	\item
	A. Anshul, \textbf{Sateesh K. Peddoju}, \lq\lq \textit{NTPDroid: A Hybrid Android Malware Detector using Network Traffic and System Permissions},\rq\rq\, in The 17th IEEE International Conference On Trust, Security And Privacy In Computing And Communications (IEEE TrustCom-18), New York, July 31 - August 3, 2018, \underline{\textbf{ERA/CORE Rank:A}}, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/TrustCom/BigDataSE.2018.00115}. \\ (Anshul Arora is the Ph. D student with Sateesh K. Peddoju)
	
	\item
	M. Santra, \textbf{Sateesh K. Peddoju}, A. K. Bhattacharjee, and A. Khan, \lq\lq \textit{Design and Analysis of a Modified Remote Attestation Protocol},\rq\rq\, in The 16th IEEE International Conference On Trust, Security And Privacy In Computing And Communications (IEEE TrustCom-17), Sydney, Australia, August 1-4, 2017,  pp. 578-585, \underline{\textbf{ERA Rank:A}}, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/Trustcom/BigDataSE/ICESS.2017.287}.	\\(Monika Santra did her M. Tech. Thesis with Sateesh K. Peddoju, and Dr. A. K. Bhattacharjee and Dr. Arindam Khan are the collaborators in this research work from BARC, Mumbai, India. Dr. A. K. Bhattacharjee, is the Co-Supervisor to Monika Santra, from BARC, India)

		
	\item
	V. Mahajan and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Deployment of Intrusion Detection System in Cloud: A Performance-Based Study},\rq\rq\,  in The 16th IEEE International Conference On Trust, Security And Privacy In Computing And Communications (IEEE TrustCom - 17), Sydney, Australia, August 1-4, 2017,  pp. 1103-1108. \underline{\textbf{ERA Rank:A}}, \textbf{IEEE}. \\ DOI: \url{https://doi.org/10.1109/Trustcom/BigDataSE/ICESS.2017.359}. \\(Varun Mahajan did his M. Tech. Thesis with Sateesh K. Peddoju)

	
	\item
	A. Ravi and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Energy-Service Trade-Off Model for Mobile Cloud Computing},\rq\rq\, in 2017 IEEE 14th International Conference on Mobile Ad Hoc and Sensor Systems (MASS), Orlando, USA, October 22-25, 2017, pp. 616-621, \underline{\textbf{ERA Rank:B}}, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/MASS.2017.64}. \\(Anuradha Ravi did her Ph. D Thesis with Sateesh K. Peddoju)

	
		\item
	A. Chaudhary, \textbf{Sateesh K. Peddoju}, and K. Kadarla, \lq\lq \textit{Study of Internet-of-Things Messaging Protocols Used for Exchanging Data with External Sources},\rq\rq\,in 2017 IEEE 14th International Conference on Mobile Ad Hoc and Sensor Systems (MASS), Orlando, USA, October 22-25, 2017, pp. 666-671, \underline{\textbf{ERA Rank:B}}, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/MASS.2017.85}. \\(Ajay Chaudhary is the Ph. D student with Sateesh K. Peddoju, Kavitha Kadarla is the fellow lab-mate and research scholar)

	
	\item
	A. Kuity and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Performance Evaluation of Container-Based High Performance Computing Ecosystem Using OpenPOWER},\rq\rq\, in The International Supercomputing Conference (ISC) High Performance 2017 (31st edition), Frankfurt, Germany, June 18-22, 2017, Lecture Notes in Computer Science \textbf{(LNCS)}, vol 10524, pp. 290-308,  \underline{\textbf{ERA Rank: C}}, \textbf{Springer}. \\DOI: \url{https://doi.org/10.1007/978-3-319-67630-2_22}. \\(Animesh Kuity is the Ph. D student with Sateesh K. Peddoju)

	
	\item
	A. Arora and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Minimizing Network Traffic Features for Android Mobile Malware Detection},\rq\rq\, in The 18th International Conference on Distributed Computing and Networking (ICDCN), Hyderabad, India, January 4-7, 2017, Article 32 (10 pages), \underline{\textbf{ERA Rank: B}}, \textbf{ACM}.  \\DOI: \url{https://doi.org/10.1145/3007748.3007763}. \\ (Anshul Arora is the Ph. D student with Sateesh K. Peddoju)

	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mask Region Grow segmentation algorithm for low-computing devices},\rq\rq\, in 22nd National Conference on Communication (NCC), \textbf{IIT Guwahati}, India, March 4-6, 2016, pp. 1-6, \underline{\textbf{ERA Rank: B}}, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/NCC.2016.7561200}. \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

	
	\item
	P. Deshpande, S. Sharma, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Data Storage Security in Cloud Paradigm},\rq\rq\, in The 5th International Conference on Soft Computing for Problem Solving (SocPros-2016), \textbf{IIT Roorkee}, India, December 23-4, 2016, pp. 247-259, The Advances in Intelligent Systems and Computing (AISC), Volume 436,  \textbf{Springer}. \\DOI:
\url{https://doi.org/10.1007/978-981-10-0448-3_20}. \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)

	
	\item
	A. Sharma and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Response time based load balancing in cloud computing},\rq\rq in The International Conference on Control, Instrumentation, Communication and Computational Technologies (ICCICCT-2014), Kanyakumari, India, July 10-11, 2014, pp. 1287-1293, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/ICCICCT.2014.6993159}. \\(Agraj Sharma did his M. Tech. Thesis with Sateesh K. Peddoju)

	
	\item
	A. Ravi and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Mobility managed energy efficient Android mobile devices using cloudlet},\rq\rq\, in Students' Technology Symposium (TechSym-2014), \textbf{IIT Kharagpur}, India, February 28 - March 2, 2014, pp. 402-407,  \textbf{IEEE}, \underline{\textbf{Best Presentation Award}}. \\DOI: \url{https://doi.org/10.1109/TechSym.2014.6808085}. \\(Dr. Anuradha Ravi did her Ph. D Thesis with Sateesh K. Peddoju)

	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mobile Mixed Reality Based Damage Level Estimation of Diseased Plant Leaf},\rq\rq\, in The 8th International Conference on Next Generation Mobile Apps, Services and Technologies (NGMAST),\textbf{Oxford University}, UK, September 10-12, 2014, pp. 72-77, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/NGMAST.2014.56}. \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

		
	\item
	A. Arora, S. Garg, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Malware detection using network traffic analysis in android based mobile devices},\rq\rq\,in The 8th International Conference on Next Generation Mobile Apps, Services and Technologies (NGMAST), \textbf{Oxford University}, UK, September 10-12, 2014, pp. 66-71, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/NGMAST.2014.57}. \\ (Anshul Arora did his  M. Tech. thesis with Sateesh K. Peddoju and Dr. Shree Garg did her Ph. D thesis work with Sateesh K. Peddoju (Co-supervisor))

	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Energy efficient mobile vision system for plant leaf disease identification},\rq\rq\, in Wireless Communications and Networking Conference (WCNC), Istanbul, Turkey, April 6-9, 2014, pp. 3314-3319, \underline{\textbf{ERA Rank: B}}, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/WCNC.2014.6953083}. \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

	
	\item
	M. H. Kumar and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Energy efficient task scheduling for parallel workflows in cloud environment},\rq\rq\, in The International Conference on Control, Instrumentation, Communication and Computational Technologies (ICCICCT-2014), Kanyakumari, India, July 10-11, 2014, pp. 1298-1303, \textbf{IEEE}. 
\\DOI: \url{https://doi.org/10.1109/ICCICCT.2014.6993161}. \\(Mallari Harish Kumar did his M. Tech. Thesis with Sateesh K. Peddoju)
	
	\item
	G. Garkoti, \textbf{Sateesh K. Peddoju}, and R. Balasubramanian, \lq\lq \textit{Detection of insider attacks in cloud based e-healthcare environment},\rq\rq\, in The 13th International Conference on Information Technology (ICIT-2014), Bhubaneswar, India, December 22-24, 2014, pp. 195-200,  \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/ICIT.2014.43}. \\(Gaurav Gargoti did his M. Tech. Thesis with Sateesh K. Peddoju, and Dr. Balasubramanian R. is the colleague to Sateesh K. Peddoju and is a Co-Supervisor to Gaurav Gargoti)

	
	\item
	S. Garg, A. K. Sarje, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Improved detection of P2P botnets through network behavior analysis},\rq\rq\, in International Conference on Security in Computer Networks and Distributed Systems (SNDS-2014), \textbf{IIITM Trivandrum}, India, March 13-14, 2014, Communications in Computer and Information Science, vol 420, pp. 334-345, \textbf{Springer}. \\DOI: \url{https://doi.org/10.1007/978-3-642-54525-2_30}. \\(Shree Garg did her Ph. D thesis work with Dr. Anil K. Sarje.  Sateesh K. Peddoju is the colleague to Dr. Anil K. Sarje and is the Co-Supervisor to Shree Garg)

	
	\item
	S. Garg, A. Sarje, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Network traffic analysis of zeroaccess bot},\rq\rq\, in The International conference on Cyber Security, \textbf{Stanford University}, USA, May 27-31, 2014, (6 pages), \textbf{ASE}. \\Link: \href{https://pdfs.semanticscholar.org/32af/3ef10f049d7ca8e9d7240d2b0cbd94336e6c.pdf}{PDF} \\(Shree Garg did her Ph. D thesis work with Dr. Anil K. Sarje.  Sateesh K. Peddoju is the colleague to Dr. Anil K. Sarje and is the Co-Supervisor to Shree Garg)

	
	\item
	P. Deshpande, S. Sharma, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Implementation of a private cloud: a case study},\rq\rq\, in The 3rd International Conference on Soft Computing for Problem Solving (SocPros-2013), \textbf{IIT Roorkee}, India, December 26-28, 2013, Advances in Intelligent Systems and Computing, Vol 259, 2014, pp. 635-647, \textbf{Springer}. \\DOI: \url{https://doi.org/10.1007/978-81-322-1768-8_56}. \\(Prachi Deshpande did her Ph. D thesis work with Dr. Subhash C. Sharma. Sateesh K. Peddoju is the colleague to Dr. Subhash C. Sharma and is the Co-Supervisor to Prachi Deshpande)

	
	\item
	A. Ravi and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Energy efficient seamless service provisioning in mobile cloud computing},\rq\rq\, in The 7th International Symposium on Service Oriented System Engineering (SOSE), Redwood City, USA, March 25-28, 2013, pp. 463-471, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/SOSE.2013.67}. \\(Dr. Anuradha Ravi did her Ph. D Thesis with Sateesh K. Peddoju)
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mobile plant species classification: a low computational approach},\rq\rq\, in The 2nd International Conference on Image Information Processing (ICIIP-2013), Shimla, India, December 9-11, 2013, pp. 405-409, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/ICIIP.2013.6707624}. \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Unsupervised resolution independent based natural plant leaf disease segmentation approach for mobile devices},\rq\rq\, in The 5th IBM workshop on Collaborative Academia Research Exchange (CARE), New Delhi, India,  October 17-19, 2013, Article 11(4 Pages), \textbf{ACM}. \\DOI: \url{https://doi.org/10.1145/2528228.2528240}. \\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mobile augmented reality based interactive teaching \& learning system with low computation approach},\rq\rq\, in The IEEE Symposium on Computational Intelligence in Control and Automation (CICA), Singapore, April 16-19, 2013, \underline{\textbf{ERA Rank: C}}, pp. 97-103, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/CICA.2013.6611669}.\\(Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)

	
	\item
	A. Mehta, S. Prasad, and  \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Improved Connected Region Based Approach for Extraction of Principal Lines from Palm Images},\rq\rq\, in The International Conference of Image and Signal Processing, Bangalore, India, August 9-11, 2013, Science and Technology, Volume 4, pp. 104-112. \underline{\textbf{Best Paper Award}}, \textbf{Elsevier}. \\ Link: \url{https://www.searchdl.org/Resources/Public/Conf/2013/elsevierst4/ICSIP12.pdf} \\(Aditya Mehta did his M.Tech to Sateesh K. Peddoju. Shitala Prasad did his Ph. D thesis work with Sateesh K. Peddoju.) . 


	
	\item
	A. Jain, M. Mishra, \textbf{Sateesh K. Peddoju}, and N. Jain, \lq\lq \textit{Energy efficient computing-green cloud computing},\rq\rq\, in The International Conference on Energy Efficient Technologies for Sustainability (ICEETS), Nagercoil, India, April 10-12, 2013, pp. 978-982, \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/ICEETS.2013.6533519}. \\(Anubha Jain did her M. Tech. Thesis with Dr. Manoj Misra, and Sateesh K. Peddoju is the Co-Supervisor to her, Nitin Jain is the collaborator from NIT Suratkal)
	
	\item
	S. Garg, A. K. Singh, A. K. Sarje, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Behaviour analysis of machine learning algorithms for detecting P2P botnets},\rq\rq\, in The 15th international conference on Advanced computing technologies (ICACT), Rajampet, India, September 21-22, 2013, pp. 1-4,  \textbf{IEEE}. \\DOI: \url{https://doi.org/10.1109/ICACT.2013.6710523}.	\\(Shree Garg did her Ph. D thesis work with Dr. Anil K. Sarje.  Sateesh K. Peddoju is the colleague to Dr. Anil K. Sarje and is the Co-Supervisor to Shree Garg)

	
	\item
	V. Chouhan and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Hierarchical storage technique for maintaining hop-count to prevent ddos attack in cloud computing},\rq\rq\, in The International Conference on Advances in Computing, Bangalore, India, July 4-6, 2012, Advances in Intelligent Systems and Computing, Vol 174. pp. 511-518, \textbf{Springer}. \\DOI: \url{https://doi.org/10.1007/978-81-322-0740-5_62}. \\(Vikas Chouhan did his M. Tech. Thesis with Sateesh K. Peddoju)
	
	\item
	H. Verma, D. Toshniwal, and  \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Distributed frequent itemset mining framework for incremental data using MPI-style WSRF services},\rq\rq\,in The International Conference on Advances in Computing, Communications and Informatics (ICACCI-2012), Chennai, India, August 3-5, 2012, pp. 74-81, \textbf{ACM}. \\DOI: \url{https://doi.org/10.1145/2345396.2345409}. \\(Haris Verma did his M. Tech. Thesis with Dr. Durga Toshniwal, and Sateesh K. Peddoju is the Co-Supervisor to him)

	
	\item
	S. Prasad, A. Prakash, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Control of computer process using image processing and computer vision for low-processing devices},\rq\rq\, in The International Conference on Advances in Computing, Communications and Informatics (ICACCI-2012), Chennai, India, August 3-5, 2012, pp. 1169-1174, \textbf{ACM}. \\DOI: \url{https://doi.org/10.1145/2345396.2345583}. \\(Shitala Prasad did his Ph. D thesis work and Abhay Prakash did his M.Tech thesis work with Sateesh K. Peddoju, Dr. Debashis Ghosh is the colleague to Sateesh K. Peddoju and is the Co-Supervisor to Shitala Prasad)
	
%	\end{enumerate}
 \end{etaremune}