
   \begin{itemize}

	\item[\#] \textcolor{magenta}{PostDoc(s) or Equivalent Completed: 03 (details given below)}
	
	\begin{itemize}
	\item Naresh Vutukuri (3/12 Months) - PostDoc - Samsung Project - Completed.
	\item Sachi Pandey (7/12 Months) -  PostDoc -Samsung Project - Completed.
	\item Jitendar Grover (3 Years) -  Research Associate - Landslide Project - Completed.
	\end{itemize}

 %\textcolor[rgb]{0.00,0.00,1.00}
 %\textcolor{magenta}

\item[\#] \textcolor{magenta} {Ph.D.(s) Completed: 06 (details given below)}

\begin{enumerate} %[label=(PHD\arabic*).]	
		\item Anuradha Ravi (Enroll. No. 11915001): \textit{Energy Efficient Seamless Service Provisioning in Mobile Cloud Computing}; Awarded: 28-12-2015
		\item Shitala Prasad (Enroll. No. 11915006): \textit{Mobile Vision system for Plant Leaf Analysis}; Co-supervisor: Prof. D. Ghosh (ECE, IITR); Awarded: 20-02-2016
		\item Shre Garg (Enroll. No. 10915010): \textit{Network Behavior Analysis Based Effective Detection Of Botnets}; Co-supervisor: Prof. Anil K. Sarje (CSE, IITR); Awarded: 26-02-2016
		\item Prachi Deshpande (Enroll. No. 11926012): \textit{Security And Storage Issues In Cloud Environment}; Co-supervisor: Prof. S. C. Sharma (IPT, IITR); Awarded: 26-05-2016
		\item Anshul Arora (Enroll. No. 14911009): \textit{Design and Development of Models for Mobile Malware Detection}; Awarded: April 29, 2021
		\item Vikas Chouhan (Enroll. No. 14911024): \textit{Secure Deduplication, Verification, and Reliability Aspects of Cloud Storage}; Awarded: August 16, 2021
			\end{enumerate}

\item[\#] \textcolor{magenta} {Ph.D.(s) In progress: 12 (details given below)}

\begin{enumerate} %[label=(PHD\arabic*).]	
	\item Ajay Choudhary (Enroll. No. 14911016): \textit{Internet of Things (IoT) for Smart Agriculture}; Status: In Progress
	\item Animesh Kuity (Enroll. No. 15911001): \textit{High Performance Computing in Cloud};	Status: In Progress	 	
	\item Surabhi Sharma (Enroll. No. 17911010): \textit{Internet of Things (IoT) and Cloud}; Status: In Progress	
	\item Abdul Kadir (Enroll. No. 18911001), \textit{Internet of Things (IoT) and Cloud}; Status: In Progress
	\item Rama Krishna Koppanati (Enroll. No. 19911003), \textit{Security and Blockchain}; Status: In Progress	
    \item Srivastava Parth Randhir Kumar (Enroll. No. 19911011), \textit{Internet of Things (IoT) and Edge Computing}; Status: In Progress	
    \item Swati Singh (Enroll. No. 20911011), \textit{Blockchain}; Status: In Progress	
    \item Shikha Arya (Enroll. No. 20911019), \textit{Internet of Things (IoT) and Edge Computing}; Status: In Progress	
    \item Yoga B. S. (Enroll. No. RE000548), \textit{Internet of Things (IoT) and Edge Computing}; Status: In Progress	
    
    \item Suvra Pattanayak  (Enroll. No: 2291401), \textit{Cyber Security of Microgrids}; Co-supervisor: Prof. Yogesh Vijay Hote (EEE, IITR) Status: In Progress
    \item Manoj Dhaka (Enroll. No. ), \textit{Mobile Ad-hoc Networks}; Status: In Progress	 
 
			\end{enumerate}
   
%\input{../../drpskfec.github.io/_tex/phdongoing.tex}

	\item[\#] \textcolor{magenta}{M.Tech.(s) Completed: 43, In progress: 02 (details given below)}
 
%\input{../../drpskfec.github.io/_tex/mtechcompleted.tex}
%\input{mtechcompleted.tex}
%	\item[\#] M.Tech. (s) 
%\input{../../drpskfec.github.io/_tex/mtechongoing.tex}


%\textbf{2012}
\begin{enumerate} %[label=(MT\arabic*).]	
\item	(2012) Animesh Kuity : \textit{Service Level Agreement Based Grid Scheduling for Workflow Application}
\item	Ankur Jindal : \textit{An improved Backfill Algorithm in Cloud Metascheduler}
\item	Monika Choudhary : \textit{A Dynamic Algorithm for Task Scheduling in Cloud Environment}	
\item	Biswajit Sinha : \textit{Fuzzy Inference System based Reputation Model for Grid Environment} 
\item	Sonam Chugh: \textit{Access Control Based Data Security in Cloud Computing} 
\item	Anupam Burte : \textit{Virtual Machine Provisioning Based on Quality of Service Parameters}	
\item	N.V.V. Satyanarayana Reddy: \textit{Auction Based Resource Allocation in Computational Grids	} 
\item   Sri Krishna Chowdary K (IDD) : \textit{Secure Group Communication in Grid}  (Co-Supervisor: Dr. Anjali Sardana) 
\item	Harish Verma (IDD): \textit{Frequent Itemset Mining Framework Using MPI-Style WSRF Services Based on Weka4WS} (Co-Supervisor: Dr. DurgaToshniwal)
%\end{enumerate}



%\textbf{2013}



%\begin{enumerate}[label=(MT\arabic*)., resume]
\item	(2013) Tarun Sen : \textit{Identity Based Cryptography for Cloud Computing Datacenter}	 
\item	Aditya Mehta : \textit{Mobile AR System for Palm Principal Lines' Feature Extraction for Palmistry} 
\item		Mohd Junaid : \textit{Anomaly Based Intrusion Detection System for Cloud}	
\item		Nitesh Kumar Tater : \textit{Resource Provisioning in Mobile Cloud Computing using Cloudlet}
\item		Aditi : \textit{Port scanning Attack in Cloud Environment} 
\item		Ankit Jain: \textit{Offloading Android Applications to the Cloud}
\item		Shruti Jaiswal : \textit{Denial of Service Attack Modeling in Cloud Computing}
\item		Bhupendra Kumar Teli: \textit{Dynamic Resource Allocation for Mobile Applications}
\item		Jeevan Ram Meena (IDD) : \textit{A Domain Based Trust Model for Grid Environment}
\item		Anubha Jain : \textit{Improvement of Channel Bandwidth Utilization in LEACH in Wireless Sensor Network} (Co-Supervisor:	Prof. Manoj Misra)	
\item		Gyanesh Meena (IDD) : \textit{Designing an Energy Efficient Aggregation Technique for Wireless Sensor Networks} (Co-Supervisor: Dr. Vaskar Raychaudhary)
%\end{enumerate}

%\textbf{2014}

%\begin{enumerate} [label=(MT\arabic*)., resume] 

\item	(2014) Anshul Arora : \textit{Network Traffic Based Detection of Android Malwares}	
\item		Amit Ranjan : \textit{A Hierarchical Fault Tolerance Model for Cloud Systems}	
\item     Vikas Chandra Pandey: \textit{A Statistical and Distributed Packet Filter Against DDoS Attacks in Cloud Environments} 
\item		Mallari Harish Kumar : \textit{Energy Efficient Task Scheduling for Parallel Workflows in Cloud Environment}	
\item		Agraj Sharma : \textit{Response Time Based Load Balancing in Cloud Computing} 
\item		Gaurav Garkoti: \textit{Detection of Insider Attacks in Cloud Based e-Healthcare Environment} (Co-Supervisor: Dr. Balasubramanian R)
%\end{enumerate}

%\textbf{2015}

%\begin{enumerate} [label=(MT\arabic*)., resume] 
\item	(2015) Utpal Chowdhury : \textit{Detection of DDoS Attacks in Cloud Environment using Collaborative Training}
\item		Anil Pal : \textit{Reducing Frame Loss And Time In Mobile Video Transmission From Cloud}	
\item		NayanVinodkumar Intwala (IDD) : \textit{An Effective, Efficient And Highly Extensible Framework For Security-As-A-Service}	
%\end{enumerate}

%\textbf{2016}

%\begin{enumerate} [label=(MT\arabic*)., resume] 
\item	(2016) Raunak Lakhwani : \textit{Fault Tolerant Convergent Key Management in Object-based Storage}
\item		Jitender Kiraria : \textit{A Framework For Secure Transcoding Of Videos In Cloud Infrastructures}
\item		Amit Kewal: \textit{Minimizing The Response Time Of Video Streaming Using Cloudlet}
\item		Vijay Patidar : \textit{Offline De-Duplication On Encrypted Data Using Object Storage}	
%\end{enumerate}

%\textbf{2017}

%\begin{enumerate} [label=(MT\arabic*)., resume] 
\item	(2017) Prakhar Dhama : \textit{Scalable Pattern Mining Algorithms for Large Scale Interval Data}
\item		Vindeep Singh : \textit{Docker Container Based Microservice Deployment and Management System}	
\item		Ankita Rani : \textit{Workload-Aware Energy Efficient Virtual Machine Placement Algorithm for Cloud}	
\item		Maj. Varun Mahajan : 	\textit{Security of Cloud Environment using IDS and Honeypot Architecture}
\item		Monika Santra : 	\textit{Design and Implementation of Remote Attestation Protocols for Servers} (Co-Supervisor:	Dr. Anup Battacharjee, BARC, Mumbai)
%\end{enumerate}

%\textbf{2019}

%\begin{enumerate} [label=(MT\arabic*)., resume] 
\item	(2019) Akriti Sood	: 	\textit{Architecture and Framework for Edge-Assisted IoT Systems}
\item		Meenakshi Raikwar: 	\textit{Design and Development of Buffering Algorithm for Edge-Assisted IoT Systems}

\item (2020) Prashanth: \textit{Malware detection using event and time based sensor data in Android devices}
\item Alamjoth Singh: \textit{Android mobile malware detection using API calls and permissions}
\item Anjana: \textit{Malware Detection in Android Applications based on API Sequence Analysis}

\item (2021) Himanshu: \textit{System Call Extraction in Android Applications for Malware Detection}

\item (2023) Anshul: \textit{Mobile Malware Detection: Ongoing}
\item Aman Kumar Malik: \textit{Mobile Malware Detection: Ongoing}
	\end{enumerate}


\end{itemize}
