%\begin{enumerate}
\begin{etaremune}
\item Devbhoomi Cyber Hackathon. Role: Principal Investigator. Funding Agencies: Mahindra, SYSTools, iHub Divyasampark, etc., Duration: 2022, Amount: approx INR 19 Lakhs.

\item Impact Analysis of Cyber Attacks on Microgrid SCADA (IACA-µG SCADA). Role: Co-Investigator. Funding Agency: CPRI. Duration: 2022-2023. Amount: approx INR 32 Lakhs.

\item Mitigation of cyber attacks in power system using non-linear control system design. Role: Co-Investigator. Funding Agency: C3iHub. Duration: 2022-2025. Amount: approx INR 25 Lakhs.

\item Post Graduate Certificate Course on Cloud Computing and DevOps in tie up with WileyNXT Technologies Ltd., New Delhi and Continuing Education Center, IIT Roorkee (Batch 1), 2021-2022, Approx. 64.6 (IITR: 32.3) Lakhs (in consultancy mode).

\item Advanced Certification Program on Cyber Security in tie up with Eckovation Technologies Ltd., New Delhi and Continuing Education Center, IIT Roorkee (Batch 1, 2, and 3), 2020-2021, Approx. 67 (IITR: 33.6) Lakhs (in consultancy mode).

\item Dynamic Detection of Android Malware using Context-based Profiling and Machine Learning, Principal Investigator, Samsung R \& D Division, Noida, 2019-2020, INR 31.42 Lakhs. 

\item Information Security Education and Awareness (ISEA), Co-Investigator, DiETY, Ministry of Information Technology, India, 2015-2022, INR 137 Lakhs. 

\item Evaluation of Design of Low-Cost Ground Instrumentation with Real-Time Monitoring for the Development of Landslide Early Warning System, Co-Investigator, NMHS, Ministry of EFCC, 2018-2021, INR 213 Lakhs.

\item Delivering Secured and Energy Efficient Multimedia streaming services anywhere and anytime for Mobile Broadband Users, Principal Investigator, Railtel Telcom, India, 2014-2016, INR 33.72 Lakhs. 

\item Energy Efficient Multimedia Cloud Services for Mobile Devices. Role: Principal Investigator. Sponsored by: IBM, USA, Duration: 2013-2016, Amount: USD 15000. 

%\end{enumerate}
\end{etaremune}